### 2014-04-15 paper/paper.tex
Some initial paper stuff

\documentclass[letterpaper,12pt]{article}
% define the title
\usepackage{subfig}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{array}

\usepackage{epigraph}
\usepackage{url}

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}
\usepackage[margin=1in]{geometry}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
\makeatother\usepackage{algorithm}
\usepackage{multirow}
\usepackage{algpseudocode}
\begin{document}
% generates the title
\bibliographystyle{acm}

\begin{titlepage}
\begin{center}

% Upper part of the page. The $'$~$'$ is needed because \\
% only works if a paragraph has started.

\textsc{\huge Bad Commit Smells}\\[0.5cm]
\textsc{ Those Who Do Not Learn From Their Commit History Will be Doomed to Revert it}\\[1.0cm]

% Author and supervisor
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
Steven \textsc{Johnson}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
Zach \textsc{Welch}
\end{flushright}
\end{minipage}\\[1.5cm]

\large University of Wisconsin \textsc{Madison}\\[1.5cm]

\begin{abstract}
THIS SHOULD BE OUR ABSTRACT
\end{abstract}

\vfill

% Bottom of the page
{\large \today}

\end{center}
\end{titlepage}

% insert the table of contents
\tableofcontents
\listoffigures
\listoftables
\epigraph{Yeah Science!!}{ \textup{Jesse Pinkman}}

\section{Introduction}
\section{Related Work}
\section{Approach}

\bibliography{Master}

% that`s all folks
\end{document}

### 2014-04-15 source/EM.py

@@ -1,0 +1,24 @@
+import sys
+
+def EM(L,U,maxIter,threshold):
+    #L and U are lists of tuples L being labeled data and U being unlabeled data.
+    #maxIter is the maximum number of iterations, -1 means dont stop
+    #threshold is the log linear threshold difference at which to stop
+    
+    ndx = -1
+    diff = None
+    while ndx < maxIter and threshold > diff:
+        if maxIter>0:
+            ndx=ndx+1
+
+        update = #some update step
+
+        
+        
+
+
+
+
+
+
+

### 2014-04-17 source/EM.py
a non tested but syntactically correct first try. possibly some labaled weighting errors

@@ -1,19 +1,89 @@
 import sys
+import numpy as np
+import math
 
-def EM(L,U,maxIter,threshold):
+
+def Normal(Mu,Sigma,X):
+    math.exp(-.5*(x-Mu)*Sigma.I*(x-Mu).T)/sqrt((2*math.pi)**len(X)*np.linalg.det(Sigma))    
+
+def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     #L and U are lists of tuples L being labeled data and U being unlabeled data.
     #maxIter is the maximum number of iterations, -1 means dont stop
     #threshold is the log linear threshold difference at which to stop
     
+    
+    #Init using only labeled data
+    Ycounts  = [0.0,0.0]
+
+    for l in L:
+        Ycounts[Ys.find(l[1])]= Ycounts[Ys.find(l[1])]+1
+
+
+    Mus    = []
+    Sigmas = []
+    for yNdx in range(len(Ys)):
+        Mu = mat(zeros(len(L[0][0].keys())))
+        Sigma=mat(zeros([len(L[0][0].keys()),len(L[0][0].keys())]))
+        for lNdx in range(len(L)):
+            if Ys[yNdx] == L[lNdx][1]:        
+                Mu = Mu + Wl[lNdx]*l[lNdx][0].values()
+        Mu = Mu/Ycounts[yNdx]
+
+        for lNdx in range(len(L)):
+            if Ys[yNdx] == L[lNdx][1]:        
+                Sigma = Sigma + (Wl[lNdx]*L[lNdx][0].values()-Mu).T*(Wl[lNdx]*L[lNdx][0].values()-Mu)
+        Sigma = Sigma/Ycounts[yNdx]
+
+        Mus.append(Mu)
+        Sigmas.append(Sigma)
+
+    l = Ycounts[0]+Ycounts[1]
+    Pi = [Ycounts[0]/l,Ycounts[1]/l]
+
     ndx = -1
     diff = None
     while ndx < maxIter and threshold > diff:
         if maxIter>0:
             ndx=ndx+1
 
-        update = #some update step
+        #E step
+        gammas = matrix(zeros(len(U),len(Ys)))
+        for uNdx in range(len(U)):
+            for yNdx in len(Range(Ys)):
+                gammas[uNdx][yNdx] = Pi[yNdx]*Normal(Mus[yNdx],Sigmas[yNdx],U[uNdx][0].values())
[…]

### 2014-04-18 source/EM.py
Pretty much done; need to add log likelihood and run some more tests

@@ -3,8 +3,8 @@ import numpy as np
 import math
 
 
-def Normal(Mu,Sigma,X):
-    math.exp(-.5*(x-Mu)*Sigma.I*(x-Mu).T)/sqrt((2*math.pi)**len(X)*np.linalg.det(Sigma))    
+def Normal(Mu,Sigma,x):
+    return math.exp(-.5*(x-Mu)*Sigma.I*(x-Mu).T)/math.sqrt((2*math.pi)**len(x)*np.linalg.det(Sigma))    
 
 def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     #L and U are lists of tuples L being labeled data and U being unlabeled data.
@@ -14,77 +14,107 @@ def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     
     #Init using only labeled data
     Ycounts  = [0.0,0.0]
-
+    Wlcounts = [0.0,0.0]
     for l in L:
-        Ycounts[Ys.find(l[1])]= Ycounts[Ys.find(l[1])]+1
-
+        Ycounts[Ys.index(l[1])]= Ycounts[Ys.index(l[1])]+1
+        Wlcounts[Ys.index(l[1])]=Wlcounts[Ys.index(l[1])]+Wl[L.index(l)]
 
     Mus    = []
     Sigmas = []
     for yNdx in range(len(Ys)):
-        Mu = mat(zeros(len(L[0][0].keys())))
-        Sigma=mat(zeros([len(L[0][0].keys()),len(L[0][0].keys())]))
+        effW = Ycounts[yNdx]/Wlcounts[yNdx]
+        Mu = np.mat(np.zeros(len(L[0][0].keys())))
+        Sigma=np.mat(np.zeros([len(L[0][0].keys()),len(L[0][0].keys())]))
         for lNdx in range(len(L)):
-            if Ys[yNdx] == L[lNdx][1]:        
-                Mu = Mu + Wl[lNdx]*l[lNdx][0].values()
+            if Ys[yNdx] == L[lNdx][1]:
+                X = np.matrix(L[lNdx][0].values())       
+                Mu = Mu + Wl[lNdx]*effW*X
         Mu = Mu/Ycounts[yNdx]
 
         for lNdx in range(len(L)):
             if Ys[yNdx] == L[lNdx][1]:        
-                Sigma = Sigma + (Wl[lNdx]*L[lNdx][0].values()-Mu).T*(Wl[lNdx]*L[lNdx][0].values()-Mu)
[…]

### 2014-05-02 source/EM.py
some bullshit i hadta fix

@@ -9,9 +9,8 @@ from weka import Weka
 
 def Normal(Mu,Sigma,x):
     try:
-        val= math.exp(-math.fabs(5*(x-Mu)*Sigma.I*(x-Mu).T))/math.sqrt((2*math.pi)**len(x)*math.fabs(np.linalg.det(Sigma)))    
+        val= math.exp(-math.fabs(0.5*(x-Mu)*Sigma.I*(x-Mu).T))/math.sqrt((2*math.pi)**len(x)*math.fabs(np.linalg.det(Sigma)))    
     except :
-        #print 'Warning, singular matrix'
         val =0.0
     return val
 
@@ -26,9 +25,13 @@ def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     #threshold is the log linear threshold difference at which to stop
     
     #Init using only labeled data
+    Wl = []
+    Wu = []
 
-    if len(U) == 0:
-        return []
+    for i in xrange(len(L)):
+        Wl.append(1.0/len(L))
+    for i in xrange(len(U)):
+        Wu.append(1.0/len(U))
 
     Ycounts  = [0.0,0.0]
     Wlcounts = [0.0,0.0]
@@ -39,23 +42,20 @@ def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     Mus    = []
     Sigmas = []
     for yNdx in range(len(Ys)):
-        effW = 0.0
-        if Wlcounts[yNdx]:
-            effW = Ycounts[yNdx]/Wlcounts[yNdx]
         Mu = np.mat(np.zeros(len(L[0][0].keys())))
         Sigma=np.mat(np.zeros([len(L[0][0].keys()),len(L[0][0].keys())]))
         for lNdx in range(len(L)):
             if Ys[yNdx] == L[lNdx][1]:
                 X = np.matrix(L[lNdx][0].values())
 
-                Mu = Mu + (Wl[lNdx]*effW)*X
+                Mu = Mu + (Wl[lNdx]*len(L))*X#effW)*X
         if Ycounts[yNdx]:
             Mu = Mu/Ycounts[yNdx]
 
         for lNdx in range(len(L)):
             if Ys[yNdx] == L[lNdx][1]:        
                 X = np.matrix(L[lNdx][0].values())       
[…]

### 2014-05-04 paper/paper.tex

@@
-\documentclass[letterpaper,12pt]{article}
-% define the title
-\usepackage{subfig}
+% This is "sig-alternate.tex" V2.0 May 2012
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.5 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V2.0 - May 2012
 
-\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{multirow}
-\usepackage{array}
+\documentclass{sig-alternate}
 
-\usepackage{epigraph}
-\usepackage{url}
+\begin{document}
+%
+% --- Author Metadata here ---
+\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
 
-% \epigraphsize{\small}% Default
-\setlength\epigraphwidth{16cm}
-\setlength\epigraphrule{1pt}
-\usepackage[margin=1in]{geometry}
+\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
+Format\titlenote{(Produces the permission block, and
+copyright information). For use with
+SIG-ALTERNATE.CLS. Supported by ACM.}}
+\subtitle{[Extended Abstract]
+\titlenote{A full version of this paper is available as
+\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+\LaTeX$2_\epsilon$\ and BibTeX} at
+\texttt{www.acm.org/eaddress.htm}}}
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
-\makeatother\usepackage{algorithm}
-\usepackage{multirow}
-\usepackage{algpseudocode}
-\begin{document}
-% generates the title
-\bibliographystyle{acm}
+\numberofauthors{8} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{1932 Wallamaloo Lane}\\
+       \affaddr{Wallamaloo, New Zealand}\\
+       \email{trovato@corporation.com}
+% 2nd. author
+\alignauthor
+G.K.M. Tobin\titlenote{The secretary disavows
+any knowledge of this author's actions.}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{P.O. Box 1212}\\
+       \affaddr{Dublin, Ohio 43017-6221}\\
+       \email{webmaster@marysville-ohio.com}
+% 3rd. author
+\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
+one who did all the really hard work.}\\
+       \affaddr{The Th{\o}rv{\"a}ld Group}\\
+       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+       \affaddr{Hekla, Iceland}\\
+       \email{larst@affiliation.org}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor Lawrence P. Leipuner\\
+       \affaddr{Brookhaven Laboratories}\\
+       \affaddr{Brookhaven National Lab}\\
+       \affaddr{P.O. Box 5000}\\
+       \email{lleipuner@researchlabs.org}
+% 5th. author
+\alignauthor Sean Fogarty\\
+       \affaddr{NASA Ames Research Center}\\
+       \affaddr{Moffett Field}\\
+       \affaddr{California 94035}\\
+       \email{fogartys@amesres.org}
+% 6th. author
+\alignauthor Charles Palmer\\
+       \affaddr{Palmer Research Laboratories}\\
+       \affaddr{8600 Datapoint Drive}\\
+       \affaddr{San Antonio, Texas 78229}\\
+       \email{cpalmer@prl.com}
+}
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
+email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
+\date{30 July 1999}
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
-\begin{titlepage}
-\begin{center}
+\maketitle
+\begin{abstract}
+This paper provides a sample of a \LaTeX\ document which conforms,
+somewhat loosely, to the formatting guidelines for
+ACM SIG Proceedings. It is an {\em alternate} style which produces
+a {\em tighter-looking} paper and was designed in response to
+concerns expressed, by authors, over page-budgets.
+It complements the document \textit{Author's (Alternate) Guide to
+Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
+This source file has been written with the intention of being
+compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-% Upper part of the page. The $'$~$'$ is needed because \\
-% only works if a paragraph has started.
+The developers have tried to include every imaginable sort
+of ``bells and whistles", such as a subtitle, footnotes on
+title, subtitle and authors, as well as in the text, and
+every optional component (e.g. Acknowledgments, Additional
+Authors, Appendices), not to mention examples of
+equations, theorems, tables and figures.
 
-\textsc{\huge Bad Commit Smells}\\[0.5cm]
-\textsc{ Those Who Do Not Learn From Their Commit History Will be Doomed to Revert it}\\[1.0cm]
-
-% Author and supervisor
-\begin{minipage}{0.4\textwidth}
-\begin{flushleft} \large
-Steven \textsc{Johnson}
-\end{flushleft}
-\end{minipage}
-\begin{minipage}{0.4\textwidth}
-\begin{flushright} \large
-Zach \textsc{Welch}
-\end{flushright}
-\end{minipage}\\[1.5cm]
-
-\large University of Wisconsin \textsc{Madison}\\[1.5cm]
-
-\begin{abstract}
-THIS SHOULD BE OUR ABSTRACT
+To make best use of this sample document, run it through \LaTeX\
+and BibTeX, and compare this source code with the printed
+output produced by the dvi file. A compiled PDF version
+is available on the web page to help you with the
+`look and feel'.
 \end{abstract}
 
-\vfill
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-% Bottom of the page
-{\large \today}
+\terms{Theory}
 
-\end{center}
-\end{titlepage}
-
-% insert the table of contents
-\tableofcontents
-\listoffigures
-\listoftables
-\epigraph{Yeah Science!!}{ \textup{Jesse Pinkman}}
+\keywords{ACM proceedings, \LaTeX, text tagging}
 
 \section{Introduction}
-\section{Related Work}
-\section{Approach}
+The \textit{proceedings} are the records of a conference.
+ACM seeks to give these conference by-products a uniform,
+high-quality appearance.  To do this, ACM has some rigid
+requirements for the format of the proceedings documents: there
+is a specified format (balanced  double columns), a specified
+set of fonts (Arial or Helvetica and Times Roman) in
+certain specified sizes (for instance, 9 point for body copy),
+a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
+the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
+and (1.9 cm [.75"]) left and right; specified column width
+(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
 
-\bibliography{Master}
+The good news is, with only a handful of manual
+settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
+and {\texttt{\char'134 alignauthor}} commands, you have
+already used; another, {\texttt{\char'134 balancecolumns}}, will
+be used in your very last run of \LaTeX\ to ensure
+balanced column heights on the last page.}, the \LaTeX\ document
+class file handles all of this for you.
 
-% that`s all folks
+The remainder of this document is concerned with showing, in
+the context of an ``actual'' document, the \LaTeX\ commands
+specifically available for denoting the structure of a
+proceedings paper, rather than with giving rigorous descriptions
+or explanations of such commands.
+
+\section{The {\secit Body} of The Paper}
+Typically, the body of a paper is organized
+into a hierarchical structure, with numbered or unnumbered
+headings for sections, subsections, sub-subsections, and even
+smaller sections.  The command \texttt{{\char'134}section} that
+precedes this paragraph is part of such a
+hierarchy.\footnote{This is the second footnote.  It
+starts a series of three footnotes that add nothing
+informational, but just give an idea of how footnotes work
+and look. It is a wordy one, just so you see
+how a longish one plays out.} \LaTeX\ handles the numbering
+and placement of these headings for you, when you use
+the appropriate heading commands around the titles
+of the headings.  If you want a sub-subsection or
+smaller part to be unnumbered in your output, simply append an
+asterisk to the command name.  Examples of both
+numbered and unnumbered headings will appear throughout the
+balance of this sample document.
+
+Because the entire article is contained in
+the \textbf{document} environment, you can indicate the
+start of a new paragraph with a blank line in your
+input file; that is why this sentence forms a separate paragraph.
+
+\subsection{Type Changes and {\subsecit Special} Characters}
+We have already seen several typeface changes in this sample.  You
+can indicate italicized words or phrases in your text with
+the command \texttt{{\char'134}textit}; emboldening with the
+command \texttt{{\char'134}textbf}
+and typewriter-style (for instance, for computer code) with
+\texttt{{\char'134}texttt}.  But remember, you do not
+have to indicate typestyle changes when such changes are
+part of the \textit{structural} elements of your
+article; for instance, the heading of this subsection will
+be in a sans serif\footnote{A third footnote, here.
+Let's make this a rather short one to
+see how it looks.} typeface, but that is handled by the
+document class file. Take care with the use
+of\footnote{A fourth, and last, footnote.}
+the curly braces in typeface changes; they mark
+the beginning and end of
+the text that is to be in the different typeface.
+
+You can use whatever symbols, accented characters, or
+non-English characters you need anywhere in your document;
+you can find a complete list of what is
+available in the \textit{\LaTeX\
+User's Guide}\cite{Lamport:LaTeX}.
+
+\subsection{Math Equations}
+You may want to display math equations in three distinct styles:
+inline, numbered or non-numbered display.  Each of
+the three are discussed in the next sections.
+
+\subsubsection{Inline (In-text) Equations}
+A formula that appears in the running text is called an
+inline or in-text formula.  It is produced by the
+\textbf{math} environment, which can be
+invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
+construction or with the short form \texttt{\$. . .\$}. You
+can use any of the symbols and structures,
+from $\alpha$ to $\omega$, available in
+\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
+few examples of in-text equations in context. Notice how
+this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
+set here in in-line math style, looks slightly different when
+set in display style.  (See next section).
+
+\subsubsection{Display Equations}
+A numbered display equation -- one set off by vertical space
+from the text and centered horizontally -- is produced
+by the \textbf{equation} environment. An unnumbered display
+equation is produced by the \textbf{displaymath} environment.
+
+Again, in either environment, you can use any of the symbols
+and structures available in \LaTeX; this section will just
+give a couple of examples of display equations in context.
+First, consider the equation, shown as an inline equation above:
+\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
+Notice how it is formatted somewhat differently in
+the \textbf{displaymath}
+environment.  Now, we'll enter an unnumbered equation:
+\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
+and follow it with another numbered equation:
+\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
+just to demonstrate \LaTeX's able handling of numbering.
+
+\subsection{Citations}
+Citations to articles \cite{bowman:reasoning,
+clark:pct, braams:babel, herlihy:methodology},
+conference proceedings \cite{clark:pct} or
+books \cite{salas:calculus, Lamport:LaTeX} listed
+in the Bibliography section of your
+article will occur throughout the text of your article.
+You should use BibTeX to automatically produce this bibliography;
+you simply need to insert one of several citation commands with
+a key of the item cited in the proper location in
+the \texttt{.tex} file \cite{Lamport:LaTeX}.
+The key is a short reference you invent to uniquely
+identify each work; in this sample document, the key is
+the first author's surname and a
+word from the title.  This identifying key is included
+with each item in the \texttt{.bib} file for your article.
+
+The details of the construction of the \texttt{.bib} file
+are beyond the scope of this sample document, but more
+information can be found in the \textit{Author's Guide},
+and exhaustive details in the \textit{\LaTeX\ User's
+Guide}\cite{Lamport:LaTeX}.
+
+This article shows only the plainest form
+of the citation command, using \texttt{{\char'134}cite}.
+This is what is stipulated in the SIGS style specifications.
+No other citation format is endorsed or supported.
+
+\subsection{Tables}
+Because tables cannot be split across pages, the best
+placement for them is typically the top of the page
+nearest their initial cite.  To
+ensure this proper ``floating'' placement of tables, use the
+environment \textbf{table} to enclose the table's contents and
+the table caption.  The contents of the table itself must go
+in the \textbf{tabular} environment, to
+be aligned properly in rows and columns, with the desired
+horizontal and vertical rules.  Again, detailed instructions
+on \textbf{tabular} material
+is found in the \textit{\LaTeX\ User's Guide}.
+
+Immediately following this sentence is the point at which
+Table 1 is included in the input file; compare the
+placement of the table here with the table in the printed
+dvi output of this document.
+
+\begin{table}
+\centering
+\caption{Frequency of Special Characters}
+\begin{tabular}{|c|c|l|} \hline
+Non-English or Math&Frequency&Comments\\ \hline
+\O & 1 in 1,000& For Swedish names\\ \hline
+$\pi$ & 1 in 5& Common in math\\ \hline
+\$ & 4 in 5 & Used in business\\ \hline
+$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+\hline\end{tabular}
+\end{table}
+
+To set a wider table, which takes up the whole width of
+the page's live area, use the environment
+\textbf{table*} to enclose the table's contents and
+the table caption.  As with a single-column table, this wide
+table will ``float" to a location deemed more desirable.
+Immediately following this sentence is the point at which
+Table 2 is included in the input file; again, it is
+instructive to compare the placement of the
+table here with the table in the printed dvi
+output of this document.
+
+\begin{table*}
+\centering
+\caption{Some Typical Commands}
+\begin{tabular}{|c|c|l|} \hline
+Command&A Number&Comments\\ \hline
+\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
+\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
+\texttt{{\char'134}table}& 300 & For tables\\ \hline
+\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
+\end{table*}
+% end the environment with {table*}, NOTE not {table}!
+
+\subsection{Figures}
+Like tables, figures cannot be split across pages; the
+best placement for them
+is typically the top or the bottom of the page nearest
+their initial cite.  To ensure this proper ``floating'' placement
+of figures, use the environment
+\textbf{figure} to enclose the figure and its caption.
+
+This sample document contains examples of \textbf{.eps}
+and \textbf{.ps} files to be displayable with \LaTeX.  More
+details on each of these is found in the \textit{Author's Guide}.
+
+As was the case with tables, you may want a figure
+that spans two columns.  To do this, and still to
+ensure proper ``floating'' placement of tables, use the environment
+\textbf{figure*} to enclose the figure and its caption.
+and don't forget to end the environment with
+{figure*}, not {figure}!
+
+Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
+used; use
+the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
+commands as appropriate for the different file types.
+
+\subsection{Theorem-like Constructs}
+Other common constructs that may occur in your article are
+the forms for logical constructs like theorems, axioms,
+corollaries and proofs.  There are
+two forms, one produced by the
+command \texttt{{\char'134}newtheorem} and the
+other by the command \texttt{{\char'134}newdef}; perhaps
+the clearest and easiest way to distinguish them is
+to compare the two in the output of this sample document:
+
+This uses the \textbf{theorem} environment, created by
+the\linebreak\texttt{{\char'134}newtheorem} command:
+\newtheorem{theorem}{Theorem}
+\begin{theorem}
+Let $f$ be continuous on $[a,b]$.  If $G$ is
+an antiderivative for $f$ on $[a,b]$, then
+\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
+\end{theorem}
+
+The other uses the \textbf{definition} environment, created
+by the \texttt{{\char'134}newdef} command:
+\newdef{definition}{Definition}
+\begin{definition}
+If $z$ is irrational, then by $e^z$ we mean the
+unique number which has
+logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
+\end{definition}
+
+Two lists of constructs that use one of these
+forms is given in the
+\textit{Author's  Guidelines}.
+
+There is one other similar construct environment, which is
+already set up
+for you; i.e. you must \textit{not} use
+a \texttt{{\char'134}newdef} command to
+create it: the \textbf{proof} environment.  Here
+is a example of its use:
+\begin{proof}
+Suppose on the contrary there exists a real number $L$ such that
+\begin{displaymath}
+\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
+\end{displaymath}
+Then
+\begin{displaymath}
+l=\lim_{x\rightarrow c} f(x)
+= \lim_{x\rightarrow c}
+\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
+= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
+\frac{f(x)}{g(x)} = 0\cdot L = 0,
+\end{displaymath}
+which contradicts our assumption that $l\neq 0$.
+\end{proof}
+
+Complete rules about using these environments and using the
+two different creation commands are in the
+\textit{Author's Guide}; please consult it for more
+detailed instructions.  If you need to use another construct,
+not listed therein, which you want to have the same
+formatting as the Theorem
+or the Definition\cite{salas:calculus} shown above,
+use the \texttt{{\char'134}newtheorem} or the
+\texttt{{\char'134}newdef} command,
+respectively, to create it.
+
+\subsection*{A {\secit Caveat} for the \TeX\ Expert}
+Because you have just been given permission to
+use the \texttt{{\char'134}newdef} command to create a
+new form, you might think you can
+use \TeX's \texttt{{\char'134}def} to create a
+new command: \textit{Please refrain from doing this!}
+Remember that your \LaTeX\ source code is primarily intended
+to create camera-ready copy, but may be converted
+to other forms -- e.g. HTML. If you inadvertently omit
+some or all of the \texttt{{\char'134}def}s recompilation will
+be, to say the least, problematic.
+
+\section{Conclusions}
+This paragraph will end the body of this sample document.
+Remember that you might still have Acknowledgments or
+Appendices; brief samples of these
+follow.  There is still the Bibliography to deal with; and
+we will make a disclaimer about that here: with the exception
+of the reference to the \LaTeX\ book, the citations in
+this paper are to articles which have nothing to
+do with the present subject and are used as
+examples only.
+%\end{document}  % This is where a 'short' article might terminate
+
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+This section is optional; it is a location for you
+to acknowledge grants, funding, editing assistance and
+what have you.  In the present case, for example, the
+authors would like to thank Gerald Murray of ACM for
+his help in codifying this \textit{Author's Guide}
+and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
+\appendix
+%Appendix A
+\section{Headings in Appendices}
+The rules about hierarchical headings discussed above for
+the body of the article are different in the appendices.
+In the \textbf{appendix} environment, the command
+\textbf{section} is used to
+indicate the start of each Appendix, with alphabetic order
+designation (i.e. the first is A, the second B, etc.) and
+a title (if you include one).  So, if you need
+hierarchical structure
+\textit{within} an Appendix, start with \textbf{subsection} as the
+highest level. Here is an outline of the body of this
+document in Appendix-appropriate form:
+\subsection{Introduction}
+\subsection{The Body of the Paper}
+\subsubsection{Type Changes and  Special Characters}
+\subsubsection{Math Equations}
+\paragraph{Inline (In-text) Equations}
+\paragraph{Display Equations}
+\subsubsection{Citations}
+\subsubsection{Tables}
+\subsubsection{Figures}
+\subsubsection{Theorem-like Constructs}
+\subsubsection*{A Caveat for the \TeX\ Expert}
+\subsection{Conclusions}
+\subsection{Acknowledgments}
+\subsection{Additional Authors}
+This section is inserted by \LaTeX; you do not insert it.
+You just add the names and information in the
+\texttt{{\char'134}additionalauthors} command at the start
+of the document.
+\subsection{References}
+Generated by bibtex from your ~.bib file.  Run latex,
+then bibtex, then latex twice (to resolve references)
+to create the ~.bbl file.  Insert that ~.bbl file into
+the .tex source file and comment out
+the command \texttt{{\char'134}thebibliography}.
+% This next section command marks the start of
+% Appendix B, and does not continue the present hierarchy
+\section{More Help for the Hardy}
+The sig-alternate.cls file itself is chock-full of succinct
+and helpful comments.  If you consider yourself a moderately
+experienced to expert user of \LaTeX, you may find reading
+it useful but please remember not to change it.
+%\balancecolumns % GM June 2007
+% That's all folks!
 \end{document}

### 2014-05-04 source/EM.py
lwef

@@ -25,13 +25,13 @@ def EM(L,U,Wl,Wu,Ys,maxIter,threshold):
     #threshold is the log linear threshold difference at which to stop
     
     #Init using only labeled data
-    Wl = []
-    Wu = []
+   # Wl = []
+   # Wu = []
 
-    for i in xrange(len(L)):
-        Wl.append(1.0/len(L))
-    for i in xrange(len(U)):
-        Wu.append(1.0/len(U))
+   # for i in xrange(len(L)):
+   #     Wl.append(1.0/len(L))
+   # for i in xrange(len(U)):
+   #     Wu.append(1.0/len(U))
 
     Ycounts  = [0.0,0.0]
     Wlcounts = [0.0,0.0]

### 2014-05-04 paper/paper.tex
some initial paper bs

@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+\conferenceinfo{CS 760}{'14,Madison WI, USA}
+\CopyrightYear{2014} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
 %\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
@@
 
-\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
+\title{BoostEM}
+\subtitle{A Semi-Supervised Ensemble Method}
 %
@@
 
-\numberofauthors{8} %  in this sample file, there are a *total*
+\numberofauthors{2} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+Zach Welch\\
+       \affaddr{UW-Madison}\\
+       \email{zwelch@cs.wisc.edu}
 % 2nd. author
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+Steven Johnson\\
+       \affaddr{UW-Madison}\\
+       \email{sjj@cs.wisc.edu}
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
+\date{May 12, 2014}
 % Just remember to make sure that the TOTAL number of authors

### 2014-05-04 paper/paper.tex
some more push

--- 2014-04-15 paper/paper.tex
@@
-\documentclass[letterpaper,12pt]{article}
-% define the title
-\usepackage{subfig}
+% This is "sig-alternate.tex" V2.0 May 2012
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.5 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V2.0 - May 2012
 
-\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{multirow}
-\usepackage{array}
+\documentclass{sig-alternate}
 
-\usepackage{epigraph}
-\usepackage{url}
+\begin{document}
+%
+% --- Author Metadata here ---
+\conferenceinfo{CS 760}{'14,Madison WI, USA}
+\CopyrightYear{2014} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
 
-% \epigraphsize{\small}% Default
-\setlength\epigraphwidth{16cm}
-\setlength\epigraphrule{1pt}
-\usepackage[margin=1in]{geometry}
+\title{BoostEM}
+\subtitle{A Semi-Supervised Ensemble Method}
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
-\makeatother\usepackage{algorithm}
-\usepackage{multirow}
-\usepackage{algpseudocode}
-\begin{document}
-% generates the title
-\bibliographystyle{acm}
+\numberofauthors{2} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Zach Welch\\
+       \affaddr{UW-Madison}\\
+       \email{zwelch@cs.wisc.edu}
+% 2nd. author
+\alignauthor
+Steven Johnson\\
+       \affaddr{UW-Madison}\\
+       \email{sjj@cs.wisc.edu}
+}
+\date{May 12, 2014}
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
-\begin{titlepage}
-\begin{center}
-
-% Upper part of the page. The $'$~$'$ is needed because \\
-% only works if a paragraph has started.
-
-\textsc{\huge Bad Commit Smells}\\[0.5cm]
-\textsc{ Those Who Do Not Learn From Their Commit History Will be Doomed to Revert it}\\[1.0cm]
-
-% Author and supervisor
-\begin{minipage}{0.4\textwidth}
-\begin{flushleft} \large
-Steven \textsc{Johnson}
-\end{flushleft}
-\end{minipage}
-\begin{minipage}{0.4\textwidth}
-\begin{flushright} \large
-Zach \textsc{Welch}
-\end{flushright}
-\end{minipage}\\[1.5cm]
-
-\large University of Wisconsin \textsc{Madison}\\[1.5cm]
-
+\maketitle
 \begin{abstract}
-THIS SHOULD BE OUR ABSTRACT
+We introduce BoostEM, a semi-supervised learning algorithm which combines the benefits of using an ensemble method like Boosting with the benefits of using unlabeled data.
+BoostEM is intended for use in learning settings with an abundance of unlabeled data, and outperforms the traditional AdaBoost algorithm and learning with fractional data from using Expectation Maximization across a variety of base learners and data sets.
 \end{abstract}
 
-\vfill
+% A category with the (minimum) three required fields
+\section{Introduction}
+STEVE
+\section{Background}
+\subsection{Boost}
+\subsection{Expectation Maximization}
+\section{Related Work}
+\section{BoostEM}
+\section{Evaluation}
+\subsection{Methodology}
+STEVE
+\subsection{Results}
+\section{Discussion}
+STEVE 
+\section{Conclusions}
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
 
-% Bottom of the page
-{\large \today}
+\bibliographystyle{abbrv}
+\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
 
-\end{center}
-\end{titlepage}
-
-% insert the table of contents
-\tableofcontents
-\listoffigures
-\listoftables
-\epigraph{Yeah Science!!}{ \textup{Jesse Pinkman}}
-
-\section{Introduction}
-\section{Related Work}
-\section{Approach}
-
-\bibliography{Master}
-
-% that`s all folks
 \end{document}

### 2014-05-05 paper/paper.tex
some stuff

@@
 \documentclass{sig-alternate}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 \subsection{Expectation Maximization}
+Expectation is an iterative algorithm which uses the values of existing,complete data points to compute the maximum likelihood estimate for missing values for other, incomplete data.
+Expectation Maximization was originally introduced in ~\cite{Dempster77maximumlikelihood} and produces a probabalistic distribution of the possible values of missing data given fully labeled data.
+In the context of semi-supervised learning, there is a set of labeled input data and a potentially much larger set of unlabeled data and for each unlabeled instance u, EM can provide a probability for each label.
+These probabilities can be used as fractional instances of labeled data, making the input training set much bigger and diverse and potentially giving a better approximation of the distribution of labels to the learner.
+In many cases, performance can be drastically improved by using these fractional counts.
+
+Expectation maximization is a general approach and can be augmented to suite a variety of settings and assumptions.
+For instance, in our implementation of BoostEM we assume the data is well modeled by a Gaussian mixture model and the instances have weights associated with them.
+
 \section{Related Work}
 \section{BoostEM}
+The main insight of BoostEM is observing that Boost and Expectation Maximization both attempt to improve the current iteration's results by using information from the previous iteration; BoostEM simply couples the results of the two algorithms together to improve results.
+BoostEM uses a weighted EM algorithm, and these weights are identical to the weights used in the Boost algorithm.
+At it's most basic level, BoostEM simply runs a weighted Expectation Maximization on the unlabeled instances, and uses the fractional counts to create a weighted training set for some base learner.
+The results of this base learner are then used to update the weights, which are then input to EM in the next iteration.
+
+\begin{algorithm}
+\caption{BoostEM}\label{euclid}
+\begin{algorithmic}[1]
+\Procedure{BoostEM}{$L,U,T$}
+\For{$t=1 \dots T$}
+\State $P_{t} \gets EM(L,U,Wl,Wu)$
+\EndFor
+\State \textbf{return} $b$
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+By using a weighted EM, we can place more emphasis on the instances our learner incorrectly classifies in the Gaussian distribution of instances we assume.
+Or more correctly, since there is no ground truth to the unlabeled instances, we can penalize every prediction from learner $H$ on unlabeled instance $x$ by $1-p(H(x))$, where $p(\dot)$ is the distribution of labels from EM.
+In this way, the learner penalizes unexpected labels (ones with small probability) more than expected ones.
+
+Notice as well that using Expectation Maximization for fractional counts and adaBoost can be recovered from BoostEM by setting certain inputs and parameters.
+Setting the number of boosting iterations to 1 is equivalent to EM, while inputting no unlabeled instances reduces to traditional labeled Boosting.
+
 \section{Evaluation}
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 

### 2014-05-07 paper/paper.tex
some other stuff

@@
 % --- Author Metadata here ---
-\conferenceinfo{CS 760}{'14,Madison WI, USA}
+\conferenceinfo{CS 760}{'14, Madison WI, USA}
 \CopyrightYear{2014} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 Zach Welch\\
-       \affaddr{UW-Madison}\\
+       \affaddr{UW--Madison}\\
        \email{zwelch@cs.wisc.edu}
@@
 Steven Johnson\\
-       \affaddr{UW-Madison}\\
+       \affaddr{UW--Madison}\\
        \email{sjj@cs.wisc.edu}
@@
 \section{Introduction}
-STEVE
+
+It is well established in Machine Learning that labels are difficult to obtain while unlabeled data are abundant in many situations where we would like to classify new instances.
+Examples of such situations are labeling x-rays as benign or malignant, tweets as instances of bullying, news articles as interesting to a given reader, or whether a photograph contains a given object.
+Because of this scarcity of labeled instances, using semi-supervised learning techniques, such as Expectation Maximization, to combine unlabeled and labeled data into an integrated model is a good idea to potentially improve learner accuracy and reduce human labour.
+
+This paper describes the development and evaluation of a semi-supervised learning algorithm, BoostEM, which combines the benefits of an ensemble method like Boosting with the benefits of using unlabeled data.
+The next section provides an overview of related work on Boosting and Expectation Maximization.
+This section is followed by the details of the BoostEM algorithm and an experimental evaluation of our implementation.
+We then present the results of our evaluation and discuss our findings and their implications.
+
 \section{Background}
@@
 \section{Evaluation}
+We implemented the BoostEM algorithm in \textsc{python} and evaluated its accuracy against a number of other algorithms using two learners and a variety of parameter settings  as described below.
+
+\subsection{Data sets}
+
+\subsection{Benchmark Algorithms}
+
 \subsection{Methodology}

### 2014-05-07 paper/paper.tex
blakhwf
soefkwelfjwe

@@
 \subsection{Results}
+
+ \begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/accDrops.pdf}
+\caption{Average decrease in 10 fold cross validation \% accuracy using ID3 from 20\% to 5\% of the data being labeled}
+\label{accDrop}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/bankAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{bankAcc}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/parkAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{parkAcc}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/breaAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{breaAcc}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/vertAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{vertAcc}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/bankAcc5.pdf}
+\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
+\label{vertAcc}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/breaAcc5.pdf}
+\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
+\label{vertAcc}
+\end{figure}
+
 \section{Discussion}

### 2014-05-07 paper/paper.tex
soefkwelfjwe
work on my sections

@@
 
+We evaluated the performance of our algorithm on four data sets from the UCI Machine Learning Repository: Breast Cancer Wisconsin (Diagnostic), which classifies digitized images of breast mass as benign or malignant; Parkinsons, which classifies biomedical voice measurements from patients as healthy or Parkinson's; Banknote Authentication, which classifies pictures of currency as genuine or foraged; and Vertebral Column, which classifies biomedical data from patients as either normal or abnormal vertebral column.
+Each dataset is for a binary classification task, and each attribute is real-valued.
+For each dataset, the number of attributes ranges from 5 to 32 and the number of instances ranges from 197 to 1372.
+
 \subsection{Benchmark Algorithms}
 
+We used five other algorithms for comparison to BoostEM to evaluate its performance. The following lists the algorithms' abbreviations as used in the graphs and discussion and describes them.
+
+\begin{enumerate}
+\item \textbf{BoostEM}: our implementation of the BoostEM algorithm
+\item \textbf{FullBoost}: applying the AdaBoost algorithm to the fully labeled dataset
+\item \textbf{justBoost} applying the AdaBoost algorithm to the fraction of the labeled dataset
+\item \textbf{justEM} applying Expectation Maximization to the fraction of the labeled dataset
+\item \textbf{full\{Algorithm A\}} applying A to the fully labeled dataset without Boosting or EM
+\item \textbf{just\{Algorithm A\}} applying A to the fraction of the labeled dataset without Boosting or EM
+\end{enumerate}
+
 \subsection{Methodology}
-STEVE
+
+We evaluated the aforementioned algorithms manipulating the following parameters.
+
+\begin{enumerate}
+\item \textbf{Dataset}: Breast Cancer Wisconsin (Diagnostic), Parkinsons, Banknote Authentication, Vertebral Column
+\item \textbf{Learner}: ID3 Decision Tree, Naive Bayes
+\item \textbf{Fraction of Labeled Instances} 5\%, 20\%
+\end{enumerate}
+
+For each combination of these parameters, we averaged the resulting accuracies of five 10-fold cross validation runs.
+
 \subsection{Results}

### 2014-05-07 paper/paper.tex
algorithm thing
initial results written

@@
 \usepackage{algpseudocode}
-
 \begin{document}
@@
 \subsection{Boost}
+
+~\cite{Freund:1997:DGO:261540.261549}
+
 \subsection{Expectation Maximization}
@@
 \begin{algorithmic}[1]
-\Procedure{BoostEM}{$L,U,T$}
+\Procedure{BoostEM}{$L,U,H,T$}
+\State L=Labeled Data
+\State U=Unlabeled Data
+\State H=Learner
+\State T=Number of Boost iterations
+
+\State for $i \in |L|$, $ Wl(i) \gets 1$
+\State for $i \in |U|$, $ Wu(i) \gets 1$
+
 \For{$t=1 \dots T$}
-\State $P_{t} \gets EM(L,U,Wl,Wu)$
+\State Normalize $Wu,Wl$
+\State get fractional counts $P_{t} \gets EM(L,U,Wl,Wu)$
+\State $H_{t} \gets \text{model learned from L, fractional counts of U}$
+\State $\epsilon_{t} = \sum_{i=1}^{|L|} Wl_{i}(1-\delta(h_{t}(L_{i}),y_{i}))$
+\State $\epsilon_{t} += \sum_{i=1}^{|U|} Wu_{i}(1-\delta(h_{t}(L_{i}),{P_{t,}}_{h_{t}(L_{i})}))$
+\State if $|U| > 0$ then $\epsilon /= 2$
+\State $\beta_{t} \gets \frac{\epsilon_{t}}{1-\epsilon_{t}}$
+\State for $i,h_{t}(L_{i} = y_{i}) \in |L| Wl(i) \gets Wl(i)*\beta_{t}$
+\State for $i \in |U|$, $Wl(i) \gets Wu(i)*\beta_{t}$
+
 \EndFor
-\State \textbf{return} $b$
+\State \textbf{return} $\arg \max_{y} \sum_{i=1}^{T}\bigg(\log(\frac{1}{\beta_{t}}\bigg) \delta(\bf{x},y)$
 \EndProcedure
@@
 \subsection{Results}
+
+ Among the six algorithms we ran cross validation for, we expected FullBoost to have the best average performance, JustAlg to
+have the worst average performance, and the other four algorithms to perform in between. In general this intuition was found to be true about FullBoost.
+FullBoost was the top performing algorithm in 15 of the 16 settings we tested, with a setting being a dataset/labeled fraction/base learner triple.
+The only algorithm to best it was BoostEM on the parkinsons data set
+with 20\% labeled data. JustAlg, however, only performed worse than all other algorithms in 5 settings. JustBoost and EM were each the worst performing algorithm
+in 5 settings.
+
+Ideally, BoostEM would in general perform better than both JustBoost and EM since it is a generalization and combination of the two techniques. This is the case, 
+with BoostEM improving over both EM and Boost in 9 settings, and performing better than EM in 15 settings, and better than justBoost in 10. In no instances is BoostEM 
+the worst performing of the three algorithms.
+
+Somewhat surprisingly, BoostEM with 20\% of the data also outperformed using all the data on the base learner in 6 out of the 8 settings we tested.
+This would seem to imply our learner can outperform a traditional base learner while only using one fifth of the labeled data.
+
+BoostEM also performs well when the amount of labeled data is decreased by a large amount (one fourth).  In most cases, BoostEM retains its accuracy better than Boost and comparably to EM.
+
+In general it seems that fluctuations in average accuracy when BoostEM uses a different base learner is mostly due to the base learner in question, as accuracy changes by BoostEM are reflected in accuracy changes using only the base learner.
 
@@
 STEVE 
+YOU COULD TALK ABOUT HOW BECAUSE BOOSTEM CAN REPLICATE BOOST AND EM THAT WE ACTUALLY COULD DO REALLY WELL
 \section{Conclusions}

### 2014-05-08 paper/paper.tex
paper update

@@
 \item \textbf{Dataset}: Breast Cancer Wisconsin (Diagnostic), Parkinsons, Banknote Authentication, Vertebral Column
-\item \textbf{Learner}: ID3 Decision Tree, Naive Bayes
+\item \textbf{Base Learner}: ID3 Decision Tree, Naive Bayes
 \item \textbf{Fraction of Labeled Instances} 5\%, 20\%
@@
 
+In our testing, we varied our results among four datasets, two base learners, and two fractions of labeled data, for a total of sixteen data set/base learner/fraction triples, which we will define as a setting.
+
+For the Parkinsons dataset, with $20\%$ of the total data being labeled and using an ID3 base learner, BoostEM achieved an average accuracy of 73.54\%, FullBoost 86.94\%, justBoost an accuracy of 33.14\%, fractional counts using EM 68.78\%, fullID3 84.86\%, and justID3 an accuracy of 33.04\% as visualized in Figure ~\ref{parkAcc}.
+With only 5\% of the total training data labeled, BoostEM increaded to 74.64\%, justBoost fell to 26.64\%, EM to 60.5\%, and justID3 managed 26.66\%.
+FullBoost and fullID3 maintained their values because their inputs were not affected by the change.
+Using instead the weka implementation of Naive Bayes, at 20\% labeled data, BoostEM's accuracy was 76.52\%, FullBoost had 69.78\%, justBoost curiously managed 74.78\%, EM 68.16\%, FullNB 70.38\%, and JustNB 71.98\%.
+At 5\% labeled data, BoostEM reached 69.24\%, JustBoost 42.06\%, EM 55.46\%, and JustBoost only 42.34\%.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/parkAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{parkAcc}
+\end{figure}
+
+Using the vertebral column data and shown in Figure ~\ref{vertAcc}, 20\% labeled data, and ID3, BoostEM: 75.28\%, FullBoost: 82.4\%, JustBoost: 72.76\%, EM: 73.78\%, FullID3 80.36\%, justID3: 72.2\%.
+Using 5\% data, BoostEM: 70.14\%, justBoost: 68.08\%, EM: 64.78\%, justID3: 68.04\%.
+Using Naive Bayes and 20\% labeled data, BoostEM: 78.34\%,FullBoost: 83.46\%, justBoost: 80.04\%, EM: 76.16\%, FullNB 77.88\%, and justNB: 78.02\%.
+Using instead 5\% labeled data BoostEM: 70.2\%, JustBoost: 78.56\%, EM: 69.44\%, and justNB: 73.56\%.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{figures/vertAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{vertAcc}
+\end{figure}
+
+Banknote authentication data can be found in Figures ~\ref{bankAcc} and ~\ref{bankAcc5}.
+At 20\% of the labeled data, BoostEM reaches 98.12\% accuracy, FullBoost is almost perfect with 99.74\%, JustBoost with 98.38\%, EM a much lower 90.9\%, FullID3 a 96.68\%, and justID3 87.46\% accuracy.
+With the smaller amount of labeled data, BoostEM averages 94.02\%, JustEM only 66.86\%, EM retains its performance with 88.62\%, and JustID3 a relatively low 62.54\%.
+Using NB instead, BoostEM had a test set accuracy of 96.12\%, FullBoost 99.18\%, JustBoost 98.52\%, EM 84.24\%, FullNB 83.86\%, and JustNB 84.38\% accuracy at one fifth labeled data.
+BoostEM had 93.08\%, JustBoost 95.08\%, EM with 84.64\%, and JustNB 83.32\% using one twentieth of the labeled information
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.25\textwidth]{figures/bankAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{bankAcc}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.25\textwidth]{figures/bankAcc5.pdf}
+\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
+\label{bankAcc5}
+\end{figure}
+
+Finaly, with the Wisconsin Breast Cancer data, using ID3 and 20\% labeled data, the average accuracies were : BoostEM 93.5\%, FullBoost 95.62\%, justBoost 77.52\%, EM 91.08\%, FullID3 92.7\%, JustID3 78.18\%.
+At 5\% labeled data the results were: BoostEM 87.78\%, JustBoost 62.96\%, EM 86.24\%, and JustID3 62.96\%.
+With Naive Bayes and 20\% labeled data: BoostEM 92.64\%, FullBoost 95.4\%, JustBoost 94.08\%, EM 91.62\%, FullNB 92.6\%, and JustNB 92.48\%.
+at 5\% labeled data these accuracies were BoostEM 86.86\%, JustBoost 74.78\%, EM 90.66\%, and JustNB 78.32\%.
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.3\textwidth]{figures/breaAcc.pdf}
+\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
+\label{breaAcc}
+\end{figure}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.3\textwidth]{figures/breaAcc5.pdf}
+\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
+\label{breaAcc5}
+\end{figure}
+
+\section{Discussion}
+STEVE 
+YOU COULD TALK ABOUT HOW BECAUSE BOOSTEM CAN REPLICATE BOOST AND EM THAT WE ACTUALLY COULD DO REALLY WELL
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/accDrops.pdf}
+\caption{Average decrease in 10 fold cross validation \% accuracy using ID3 from 20\% to 5\% of the data being labeled}
+\label{accDrop}
+\end{figure}
+
  Among the six algorithms we ran cross validation for, we expected FullBoost to have the best average performance, JustAlg to
 have the worst average performance, and the other four algorithms to perform in between. In general this intuition was found to be true about FullBoost.
-FullBoost was the top performing algorithm in 15 of the 16 settings we tested, with a setting being a dataset/labeled fraction/base learner triple.
+FullBoost was the top performing algorithm in 15 of the 16 settings we tested.
 The only algorithm to best it was BoostEM on the parkinsons data set
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/accDrops.pdf}
-\caption{Average decrease in 10 fold cross validation \% accuracy using ID3 from 20\% to 5\% of the data being labeled}
-\label{accDrop}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/bankAcc.pdf}
-\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
-\label{bankAcc}
-\end{figure}
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/parkAcc.pdf}
-\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
-\label{parkAcc}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/breaAcc.pdf}
-\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
-\label{breaAcc}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/vertAcc.pdf}
-\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
-\label{vertAcc}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/bankAcc5.pdf}
-\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
-\label{vertAcc}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{figures/breaAcc5.pdf}
-\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
-\label{vertAcc}
-\end{figure}
-
-\section{Discussion}
-STEVE 
-YOU COULD TALK ABOUT HOW BECAUSE BOOSTEM CAN REPLICATE BOOST AND EM THAT WE ACTUALLY COULD DO REALLY WELL
 \section{Conclusions}

### 2014-05-09 paper/paper.tex
some more bs

@@
 
-It is well established in Machine Learning that labels are difficult to obtain while unlabeled data are abundant in many situations where we would like to classify new instances.
+In many machine learning classification problems, labels are difficult to obtain while unlabeled data are abundant.
 Examples of such situations are labeling x-rays as benign or malignant, tweets as instances of bullying, news articles as interesting to a given reader, or whether a photograph contains a given object.
@@
 \subsection{Boost}
+Boosting is an ensemble method which uses a set of learners trained on weighted versions of a training set.
+A popular boosting algorithm is known as AdaBoost (short for Adaptive Boost) originally detailed in ~\cite{Freund:1997:DGO:261540.261549}.
+AdaBoost works by giving each training set instance a weight $W_{i}$; initially all weights are equal.
+Over some number of iterations, AdaBoost trains a base learner (ID3 decision trees, Naive Bayes, etc) proportionally to the weights of each instance.
+The weighted training set error $\epsilon$ of this base learner is calculated and if more than half of the instances by weight were incorrect AdaBoost quits.
+Otherwise, $\beta=\frac{\epsilon}{1-\epsilon}$ is applied to all of the correctly guessed instances, decreasing their weights.
+This means that in the next iteration, incorrectly classified instances will be given more importance.
+AdaBoost then essentially drives up the importance of difficult to classify training set instances in an effort to correctly learn them.
+To classify a new instance $\bf{x}$, with base learners $H_{1} \dots H_{T}$  $\arg \max_{y} \sum_{i=1}^{T}\bigg(\log(\frac{1}{\beta_{t}})\bigg) \delta(H_{t}(\bf{x}),y)$ where $\delta(a,b)$ is the indicator function.
 
-~\cite{Freund:1997:DGO:261540.261549}
+Empirical studies ~\cite{dietterich1997machine} have shown that in a large majority of instances AdaBoost improves accuracy over the base learner.
+There are a few occasions however where using Boosting can hurt performance.
+This implies that when using AdaBoost, one should take care to compare results from the combined learner to those from a base learner.
 
@@
 \EndFor
-\State \textbf{return} $\arg \max_{y} \sum_{i=1}^{T}\bigg(\log(\frac{1}{\beta_{t}}\bigg) \delta(\bf{x},y)$
+\State \textbf{return} $\arg \max_{y} \sum_{i=1}^{T}\bigg(\log(\frac{1}{\beta_{t}})\bigg) \delta(H_{t}(\bf{x}),y)$
 \EndProcedure
@@
 
+ Using an unweighted version of Expectation Maximization is possible, but since the training set data itself is not changing, the fractional counts will not change from iteration to iteration.
+By combining the AdaBoost weights with the EM algorithm, BoostEM is able to alter the distribution and get an updated set of fractional counts in each iteration of BoostEM.
 By using a weighted EM, we can place more emphasis on the instances our learner incorrectly classifies in the Gaussian distribution of instances we assume.
-Or more correctly, since there is no ground truth to the unlabeled instances, we can penalize every prediction from learner $H$ on unlabeled instance $x$ by $1-p(H(x))$, where $p(\dot)$ is the distribution of labels from EM.
+Or more correctly, since there is no ground truth to the unlabeled instances, we can penalize every prediction from learner $H$ on unlabeled instance $x$ by $1-p(H(x))$, where $p$ is the distribution of labels from EM.
 In this way, the learner penalizes unexpected labels (ones with small probability) more than expected ones.
@@
 For each dataset, the number of attributes ranges from 5 to 32 and the number of instances ranges from 197 to 1372.
+
+\subsection{Implementation Details}
+In our testing, we only attempt to test BoostEM in classification.
+Because of this, we choose to use a Gaussian mixture model as the underlying model for data.
+Given a classification label, we assume the conditional distribution of the data to be gaussian distributed.
+One of the benefits of assuming an underlying distribution in Expectation Maximization is that it allows us to use both labeled data and a potentially much larger amount of unlabeled data in the maximization step.
+This choice may not be appropriate for all data sets; we choose Gaussian mixture models because many data sets can be roughly approximated by such a model.
+A different underlying models which provides a better fit to the data will produce likely produce better results.
+An overview of EM and Gaussian Mixture Models can be found in ~\cite{zhu2009introduction}.
 
@@
 \section{Conclusions}
+We present BoostEM, a semi-supervised ensemble method.
+BoostEM works by combining fractional counts from using the Expectation Maximization algorithm with the AdaBoost ensemble method.
+We tested BoostEM on four large datasets from the UCI repository, performing 10-fold cross validation and five random restarts for EM.
+We compared using 20\% labeled data to 5\% labeled data, the rest being unalbeled and used ID3 decision trees and Naive Bayes as base learners.
+BoostEM was compared to Boosting with 100\% of the data, Boosting with only the percentage of labeled data, performing only Expectation Maximization on the unlabeled data and using the base learner, using the base learner on all the data, and finally using only the subset of unlabeled data with a base learner.
+We found that in the majority of settings, BoostEM outperforms using only Boosting or only Expectation Maximization.
+Additionally, we found that across data sets and base learners that BoostEM performs comparably to only using a base learner, but with only one fifth of the labeled data.
+Since with specific parameters, BoostEM can replicate both AdaBoost and EM, BoostEM can always achieve performance on a data set at least as well as them, and we have shown that in many cases BoostEM can also improve performance.
+
 %ACKNOWLEDGMENTS are optional
 \section{Acknowledgments}
+Zach would like to thank his cats, who only broke one of his coffee mugs in the course of this project.
 

### 2014-05-10 paper/paper.tex
yadayada

@@
 \begin{abstract}
-We introduce BoostEM, a semi-supervised learning algorithm which combines the benefits of using an ensemble method like Boosting with the benefits of using unlabeled data.
-BoostEM is intended for use in learning settings with an abundance of unlabeled data, and outperforms the traditional AdaBoost algorithm and learning with fractional data from using Expectation Maximization across a variety of base learners and data sets.
+We introduce BoostEM, a semi-supervised ensemble method which combines the benefits of using an ensemble method like Boosting with the benefits of using unlabeled data.
+BoostEM is intended for learning settings with an abundance of unlabeled data.
+By using the weights from each iteration of AdaBoost as weights in Expectation Maximization, BoostEM can refocus its underlying model of the data distribution to place more emphasis on difficult to classify instances.
+BoostEM combines AdaBoost and using fractional count data via Expectation maximization, and with specific parameters BoostEM can reduce to either algorithm.
+BoostEM  outperforms the traditional AdaBoost  and learning with fractional data from using Expectation Maximization across a variety of base learners and data sets.
+Additionally, we have found that BoostEM performs comparably to only using its base learner (ID3 decision trees and Naive Bayes were tested) with one fifth of the labeled data.
 \end{abstract}
@@
 \section{Background}
-\subsection{Boost}
+\subsection{AdaBoost}
 Boosting is an ensemble method which uses a set of learners trained on weighted versions of a training set.
@@
 Expectation Maximization was originally introduced in ~\cite{Dempster77maximumlikelihood} and produces a probabalistic distribution of the possible values of missing data given fully labeled data.
+Expectation maximization is not itself a learning algorithm in the way ID3 or Naive Bayes are, though it is often used with unlabeled data.
+
  In the context of semi-supervised learning, there is a set of labeled input data and a potentially much larger set of unlabeled data and for each unlabeled instance u, EM can provide a probability for each label.
-These probabilities can be used as fractional instances of labeled data, making the input training set much bigger and diverse and potentially giving a better approximation of the distribution of labels to the learner.
+As originally described in ~\cite{nigam2000text}, these probabilities can be used as fractional instances of labeled data, making the input training set much bigger and diverse and potentially giving a better approximation of the distribution of labels to the learner.
 In many cases, performance can be drastically improved by using these fractional counts.
+Even if the learner in question cannot handle a fractional amount of a data point (and many cannot), this can be avoided by sampling a much larger training set, with each instance existing proportional to its fractional count.
+In this way using fractional data can be roughly approximated.
 
@@
 \section{Related Work}
+Semi-supervised learning and Ensemble Methods are both extremely well studied research areas; for surveys of semi-supervised learning and ensemble methods, we direct the reader to ~\cite{zhu05survey} and ~\cite{dietterichl2002ensemble} respectively.
+
+Additionally, combining unlabeled instances with ensemble methods is not a new idea.
+Blum and Mitchell's well known Co-training algorithm  ~\cite{blum1998combining} uses two learners trained on subsets of data to improve performance with unlabeled data.
+By using the confidence of a prediction from one learner to expand the labeled training set for the other learner, overall performance can be drastically improved over using only the explicitly labeled data.
+The independence requirements for the features of the two learners are quite strong.
+
+In ~\cite{li2007improve}, the idea of using two learners with independent sets of features was extended and combined with the popular ensemble method of random forests ~\cite{breiman2001random} to create the Co-forest algorithm.
+Because Co-forests use larger numbers of classifiers instead of two, it is very unlikely the strong independence requirments from Co-training will apply, and so they are relaxed.
+
+Many semi-supervised ensemble methods, including BoostEM, use the AdaBoost algorithm due to its performance increases.
+These algorithms differ in how they assign ``effective'' class labels to the large amount of unlabeled data.
+BoostEM uses weighted Expectation Maximization to infer a probability distribution amongst labels.
+In ~\cite{bennett2002exploiting}, the ASSEMBLE algorithm generates provisional classes for unlabeled using Suport Vector Machine esque large margins on the weighted labeled instances.
+Though we have run no tests, we suspect that if our soft EM algorithm were replaced with a hard EM algorithm, BoostEM would produce similar behavior to ASSEMBLE.
+Margin assumptions are similarly used in ~\cite{grandvalet2001semi}
+
+In ~\cite{kumar2009semiboost}, the SemiBoost framework is discussed.
+SemiBoost is a general framework for integrating many graph and cluster based semi-supervised learning methods in an iterative Boosting algorithm.
+SemiBoost is very general and it is likely that implementations like ASSEMBLE and BoostEM are realizations of the SemiBoost Framework.
+
 \section{BoostEM}
@@
 \begin{algorithmic}[1]
-\Procedure{BoostEM}{$L,U,H,T$}
 \State L=Labeled Data
@@
 
+\Procedure{BoostEM}{$L,U,H,T$}
 \State for $i \in |L|$, $ Wl(i) \gets 1$
@@
 \centering
-\includegraphics[width=0.3\textwidth]{figures/parkAcc.pdf}
+\includegraphics[width=0.35\textwidth]{figures/parkAcc.pdf}
 \caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{figures/vertAcc.pdf}
+\includegraphics[width=0.35\textwidth]{figures/vertAcc.pdf}
 \caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
@@
 \centering
-\includegraphics[width=0.25\textwidth]{figures/bankAcc.pdf}
+\includegraphics[width=0.35\textwidth]{figures/bankAcc.pdf}
 \caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
@@
 \centering
-\includegraphics[width=0.25\textwidth]{figures/bankAcc5.pdf}
+\includegraphics[width=0.35\textwidth]{figures/bankAcc5.pdf}
 \caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{figures/breaAcc.pdf}
+\includegraphics[width=0.35\textwidth]{figures/breaAcc.pdf}
 \caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{figures/breaAcc5.pdf}
+\includegraphics[width=0.35\textwidth]{figures/breaAcc5.pdf}
 \caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/accDrops.pdf}
+\includegraphics[width=0.35\textwidth]{figures/accDrops.pdf}
 \caption{Average decrease in 10 fold cross validation \% accuracy using ID3 from 20\% to 5\% of the data being labeled}

### 2014-05-11 paper/paper.tex
edits

@@
 By using the weights from each iteration of AdaBoost as weights in Expectation Maximization, BoostEM can refocus its underlying model of the data distribution to place more emphasis on difficult to classify instances.
-BoostEM combines AdaBoost and using fractional count data via Expectation maximization, and with specific parameters BoostEM can reduce to either algorithm.
+BoostEM combines AdaBoost and using fractional count data via Expectation Maximization, and with specific parameters BoostEM can reduce to either algorithm.
 BoostEM outperforms the traditional AdaBoost and learning with fractional data from using Expectation Maximization across a variety of base learners and data sets.
@@
 This paper describes the development and evaluation of a semi-supervised learning algorithm, BoostEM, which combines the benefits of an ensemble method like Boosting with the benefits of using unlabeled data.
-The next section provides an overview of related work on Boosting and Expectation Maximization.
+The next section provides background information on Boosting and Expectation Maximization.
+The following section describes related work in semi-supervised learning and ensemble methods.
 This section is followed by the details of the BoostEM algorithm and an experimental evaluation of our implementation.
@@
 AdaBoost works by giving each training set instance a weight $W_{i}$; initially all weights are equal.
-Over some number of iterations, AdaBoost trains a base learner (ID3 decision trees, Naive Bayes, etc) proportionally to the weights of each instance.
+Over some number of iterations, AdaBoost trains a base learner (ID3 decision trees, Naive Bayes, etc.) proportionally to the weights of each instance.
 The weighted training set error $\epsilon$ of this base learner is calculated and if more than half of the instances by weight were incorrect AdaBoost quits.
-Otherwise, $\beta=\frac{\epsilon}{1-\epsilon}$ is applied to all of the correctly guessed instances, decreasing their weights.
+Otherwise, $\beta=\frac{\epsilon}{1-\epsilon}$ is multiplicatively applied to all of the correctly guessed instances, decreasing their weights.
 This means that in the next iteration, incorrectly classified instances will be given more importance.
@@
 
-Empirical studies ~\cite{dietterich1997machine} have shown that in a large majority of instances AdaBoost improves accuracy over the base learner.
-There are a few occasions however where using Boosting can hurt performance.
+Empirical studies~\cite{dietterich1997machine} have shown that in a large majority of instances AdaBoost improves accuracy over the base learner.
+There are a few occasions, however, where using Boosting can hurt performance.
 This implies that when using AdaBoost, one should take care to compare results from the combined learner to those from a base learner.
@@
 \subsection{Expectation Maximization}
-Expectation is an iterative algorithm which uses the values of existing,complete data points to compute the maximum likelihood estimate for missing values for other, incomplete data.
-Expectation Maximization was originally introduced in ~\cite{Dempster77maximumlikelihood} and produces a probabalistic distribution of the possible values of missing data given fully labeled data.
+Expectation is an iterative algorithm which uses the values of existing, complete data points to compute the maximum likelihood estimate for missing values for other, incomplete data.
+Expectation Maximization was originally introduced in~\cite{Dempster77maximumlikelihood} and produces a probabalistic distribution of the possible values of missing data given fully labeled data.
 Expectation maximization is not itself a learning algorithm in the way ID3 or Naive Bayes are, though it is often used with unlabeled data.
@@
 In the context of semi-supervised learning, there is a set of labeled input data and a potentially much larger set of unlabeled data and for each unlabeled instance u, EM can provide a probability for each label.
-As originally described in ~\cite{nigam2000text}, these probabilities can be used as fractional instances of labeled data, making the input training set much bigger and diverse and potentially giving a better approximation of the distribution of labels to the learner.
+As originally described in~\cite{nigam2000text}, these probabilities can be used as fractional instances of labeled data, making the input training set much bigger and diverse and potentially giving a better approximation of the distribution of labels to the learner.
 In many cases, performance can be drastically improved by using these fractional counts.
@@
 
-Expectation maximization is a general approach and can be augmented to suite a variety of settings and assumptions.
-For instance, in our implementation of BoostEM we assume the data is well modeled by a Gaussian mixture model and the instances have weights associated with them.
+Expectation maximization is a general approach and can be augmented to suit a variety of settings and assumptions.
+For instance, in our implementation of BoostEM, we assume the data is well modeled by a Gaussian mixture model and the instances have weights associated with them.
 
 \section{Related Work}
-Semi-supervised learning and Ensemble Methods are both extremely well studied research areas; for surveys of semi-supervised learning and ensemble methods, we direct the reader to ~\cite{zhu05survey} and ~\cite{dietterichl2002ensemble} respectively.
+Semi-supervised learning and Ensemble Methods are both extremely well studied research areas; for surveys of semi-supervised learning and ensemble methods, we direct the reader to ~\cite{zhu05survey} and~\cite{dietterichl2002ensemble} respectively.
 
 Additionally, combining unlabeled instances with ensemble methods is not a new idea.
-Blum and Mitchell's well known Co-training algorithm  ~\cite{blum1998combining} uses two learners trained on subsets of data to improve performance with unlabeled data.
+Blum and Mitchell's well known Co-training algorithm~\cite{blum1998combining} uses two learners trained on subsets of data to improve performance with unlabeled data.
 By using the confidence of a prediction from one learner to expand the labeled training set for the other learner, overall performance can be drastically improved over using only the explicitly labeled data.
@@
 
-In ~\cite{li2007improve}, the idea of using two learners with independent sets of features was extended and combined with the popular ensemble method of random forests ~\cite{breiman2001random} to create the Co-forest algorithm.
+In~\cite{li2007improve}, the idea of using two learners with independent sets of features was extended and combined with the popular ensemble method of random forests~\cite{breiman2001random} to create the Co-forest algorithm.
 Because Co-forests use larger numbers of classifiers instead of two, it is very unlikely the strong independence requirments from Co-training will apply, and so they are relaxed.
@@
 BoostEM uses weighted Expectation Maximization to infer a probability distribution amongst labels.
-In ~\cite{bennett2002exploiting}, the ASSEMBLE algorithm generates provisional classes for unlabeled using Suport Vector Machine esque large margins on the weighted labeled instances.
+In~\cite{bennett2002exploiting}, the ASSEMBLE algorithm generates provisional classes for unlabeled using Suport Vector Machine esque large margins on the weighted labeled instances.
 Though we have run no tests, we suspect that if our soft EM algorithm were replaced with a hard EM algorithm, BoostEM would produce similar behavior to ASSEMBLE.
-Margin assumptions are similarly used in ~\cite{grandvalet2001semi}
+Margin assumptions are similarly used in~\cite{grandvalet2001semi}
 
-In ~\cite{kumar2009semiboost}, the SemiBoost framework is discussed.
+In~\cite{kumar2009semiboost}, the SemiBoost framework is discussed.
 SemiBoost is a general framework for integrating many graph and cluster based semi-supervised learning methods in an iterative Boosting algorithm.
@@
 BoostEM uses a weighted EM algorithm, and these weights are identical to the weights used in the Boost algorithm.
-At it's most basic level, BoostEM simply runs a weighted Expectation Maximization on the unlabeled instances, and uses the fractional counts to create a weighted training set for some base learner.
+At its most basic level, BoostEM simply runs a weighted Expectation Maximization on the unlabeled instances, and uses the fractional counts to create a weighted training set for some base learner.
 The results of this base learner are then used to update the weights, which are then input to EM in the next iteration.
@@
 
-Notice as well that using Expectation Maximization for fractional counts and adaBoost can be recovered from BoostEM by setting certain inputs and parameters.
+Notice as well that using Expectation Maximization for fractional counts and AdaBoost can be recovered from BoostEM by setting certain inputs and parameters.
 Setting the number of boosting iterations to 1 is equivalent to EM, while inputting no unlabeled instances reduces to traditional labeled Boosting.
@@
 One of the benefits of assuming an underlying distribution in Expectation Maximization is that it allows us to use both labeled data and a potentially much larger amount of unlabeled data in the maximization step.
-This choice may not be appropriate for all data sets; we choose Gaussian mixture models because many data sets can be roughly approximated by such a model.
-A different underlying models which provides a better fit to the data will produce likely produce better results.
+This choice may not be appropriate for all data sets; we chose Gaussian mixture models because many data sets can be roughly approximated by such a model.
+A different underlying model which provides a better fit to the data will produce likely produce better results.
 An overview of EM and Gaussian Mixture Models can be found in ~\cite{zhu2009introduction}.
@@
 
-We used five other algorithms for comparison to BoostEM to evaluate its performance. The following lists the algorithms' abbreviations as used in the graphs and discussion and describes them.
+We used five other algorithms for comparison to BoostEM to evaluate its performance. The following lists the algorithms' abbreviations as used in the graphs and discussion section and describes them.
 
@@
 
-For the Parkinsons dataset, with $20\%$ of the total data being labeled and using an ID3 base learner, BoostEM achieved an average accuracy of 73.54\%, FullBoost 86.94\%, justBoost an accuracy of 33.14\%, fractional counts using EM 68.78\%, fullID3 84.86\%, and justID3 an accuracy of 33.04\% as visualized in Figure ~\ref{parkAcc}.
-With only 5\% of the total training data labeled, BoostEM increaded to 74.64\%, justBoost fell to 26.64\%, EM to 60.5\%, and justID3 managed 26.66\%.
+For the Parkinsons dataset, with $20\%$ of the total data being labeled and using an ID3 base learner, BoostEM achieved an average accuracy of 73.54\%, FullBoost 86.94\%, justBoost an accuracy of 33.14\%, fractional counts using EM 68.78\%, fullID3 84.86\%, and justID3 an accuracy of 33.04\% as visualized in Figure~\ref{parkAcc}.
+With only 5\% of the total training data labeled, BoostEM increased to 74.64\%, justBoost fell to 26.64\%, EM to 60.5\%, and justID3 managed 26.66\%.
 FullBoost and fullID3 maintained their values because their inputs were not affected by the change.
@@
 
-Using the vertebral column data and shown in Figure ~\ref{vertAcc}, 20\% labeled data, and ID3, BoostEM: 75.28\%, FullBoost: 82.4\%, JustBoost: 72.76\%, EM: 73.78\%, FullID3 80.36\%, justID3: 72.2\%.
+Using the vertebral column data and shown in Figure~\ref{vertAcc}, 20\% labeled data, and ID3, BoostEM: 75.28\%, FullBoost: 82.4\%, JustBoost: 72.76\%, EM: 73.78\%, FullID3 80.36\%, justID3: 72.2\%.
 Using 5\% data, BoostEM: 70.14\%, justBoost: 68.08\%, EM: 64.78\%, justID3: 68.04\%.
@@
 
-Banknote authentication data can be found in Figures ~\ref{bankAcc} and ~\ref{bankAcc5}.
+Banknote authentication data can be found in Figures~\ref{bankAcc} and~\ref{bankAcc5}.
 At 20\% of the labeled data, BoostEM reaches 98.12\% accuracy, FullBoost is almost perfect with 99.74\%, JustBoost with 98.38\%, EM a much lower 90.9\%, FullID3 a 96.68\%, and justID3 87.46\% accuracy.
@@
 Using NB instead, BoostEM had a test set accuracy of 96.12\%, FullBoost 99.18\%, JustBoost 98.52\%, EM 84.24\%, FullNB 83.86\%, and JustNB 84.38\% accuracy at one fifth labeled data.
-BoostEM had 93.08\%, JustBoost 95.08\%, EM with 84.64\%, and JustNB 83.32\% using one twentieth of the labeled information
+BoostEM had 93.08\%, JustBoost 95.08\%, EM with 84.64\%, and JustNB 83.32\% using one twentieth of the labeled information.
 \begin{figure}[ht!]
@@
 
-Finaly, with the Wisconsin Breast Cancer data, using ID3 and 20\% labeled data, the average accuracies were : BoostEM 93.5\%, FullBoost 95.62\%, justBoost 77.52\%, EM 91.08\%, FullID3 92.7\%, JustID3 78.18\%.
+Finally, with the Wisconsin Breast Cancer data, using ID3 and 20\% labeled data, the average accuracies were: BoostEM 93.5\%, FullBoost 95.62\%, justBoost 77.52\%, EM 91.08\%, FullID3 92.7\%, JustID3 78.18\%.
 At 5\% labeled data the results were: BoostEM 87.78\%, JustBoost 62.96\%, EM 86.24\%, and JustID3 62.96\%.
@@
 \section{Discussion}
-STEVE 
-YOU COULD TALK ABOUT HOW BECAUSE BOOSTEM CAN REPLICATE BOOST AND EM THAT WE ACTUALLY COULD DO REALLY WELL
 
@@
  Among the six algorithms we ran cross validation for, we expected FullBoost to have the best average performance, JustAlg to
-have the worst average performance, and the other four algorithms to perform in between. In general this intuition was found to be true about FullBoost.
+have the worst average performance, and the other four algorithms to perform in between. In general, this intuition was found to be true about FullBoost.
 FullBoost was the top performing algorithm in 15 of the 16 settings we tested.
@@
 \section{Conclusions}
-We present BoostEM, a semi-supervised ensemble method.
+We presented BoostEM, a semi-supervised ensemble method.
 BoostEM works by combining fractional counts from using the Expectation Maximization algorithm with the AdaBoost ensemble method.
 We tested BoostEM on four large datasets from the UCI repository, performing 10-fold cross validation and five random restarts for EM.
-We compared using 20\% labeled data to 5\% labeled data, the rest being unalbeled and used ID3 decision trees and Naive Bayes as base learners.
+We compared using 20\% labeled data to 5\% labeled data, the rest being unlabeled and used ID3 decision trees and Naive Bayes as base learners.
 BoostEM was compared to Boosting with 100\% of the data, Boosting with only the percentage of labeled data, performing only Expectation Maximization on the unlabeled data and using the base learner, using the base learner on all the data, and finally using only the subset of unlabeled data with a base learner.
@@
 \section{Acknowledgments}
-Zach would like to thank his cats, who only broke one of his coffee mugs in the course of this project.
+Zach would like to thank his cats, who only broke one of his coffee mugs in the course of this project. Steve would like to thank Zhi and Brandi for being in the room while he edited this paper.
 
